\documentclass[a4paper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ragged2e}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\setlength{\footskip}{4pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%---------- MARGINS ----------
\addtolength{\oddsidemargin}{-0.50in}
\addtolength{\evensidemargin}{-0.50in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%---------- SECTION TITLES ----------
\titleformat{\section}
  {\bfseries\raggedright\normalsize}
  {}{0em}{}
  [\vspace{2pt}\titlerule]

\titlespacing*{\section}
  {0pt}
  {8pt}
  {6pt}

\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-1pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\[-2pt]
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubheadingDesc}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\[-2pt]
      \textit{\small#3} & \textit{\small #4} \\[-1pt]
      \multicolumn{2}{l}{\textit{\small #5}} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-2pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.12in, label={}, itemsep=4pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=4.5pt, parsep=0pt, topsep=1pt, partopsep=0pt, leftmargin=0.20in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

\newcommand{\resumeProjectItemListStart}{\begin{itemize}[itemsep=4.5pt, parsep=0pt, topsep=1pt, partopsep=0pt, leftmargin=0.20in]}
\newcommand{\resumeProjectItemListEnd}{\end{itemize}\vspace{-4pt}}

\renewcommand{\baselinestretch}{0.94}

\begin{document}

%----------HEADER----------
\begin{center}
    \vspace{-12pt}
    \textbf{\LARGE \scshape Romain Bastiani} \\ \vspace{3pt}
    (+33) 617108406 $|$ \href{mailto:romain.bastiani.03@gmail.com}{\underline{romain.bastiani.03@gmail.com}} $|$
    \href{https://www.linkedin.com/in/romain-bastiani-118072173/}{\underline{LinkedIn}} \\ \vspace{6pt}
    \textbf{Available for a full-time Quantitative Researcher position.}
    \vspace{6pt}
\end{center}

%-----------WORK EXPERIENCE----------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheadingDesc
{Inception Technology}{Paris, France}
{Quantitative Researcher - Macro and Systematic Commodities}{July 2025 - April 2026}
{Start-up providing quantitative positioning intelligence tools to tier-1 global commodity trading houses (clients under NDA).}

\resumeItemListStart
\resumeItem{Leveraged and enhanced a \textbf{macro factor lens} to deliver structural P\&L attribution and systematic risk diagnostics for commodity derivatives portfolios.}
\resumeItem{Developed a \textbf{regime-switching scenario engine} using \textbf{Gaussian Mixture Models (GMM)} validated through \textbf{Time-Series Cross-Validation} to capture non-linear factor dependencies and quantify tail positioning risks.}
\resumeItem{\textit{Keywords: Macro Factor Modeling, Regime Detection, Gaussian Mixture Models (GMM), Time-Series Cross-Validation, Tail Risk Diagnostics.}}
\resumeItemListEnd

\resumeSubSubheading
{Quantitative Researcher Intern}{Jan 2025 - July 2025}

\resumeItemListStart
\resumeItem{Enhanced Inception's proprietary \textbf{CTA/Trend positioning model} by integrating a \textbf{Time Series Momentum (TSMOM)} framework inspired by \textbf{Moskowitz, Ooi and Pedersen (2012)} to model systematic exposure dynamics across commodity futures.}
\resumeItem{Analyzed \textbf{CFTC COT data} (Disaggregated \& Supplemental) to decompose Managed Money exposure into \textbf{CTA/Trend}, \textbf{Index Traders}, and \textbf{Discretionary} components.}
\resumeItem{Developed positioning diagnostics including \textbf{capacity utilization}, \textbf{saturation zones}, and \textbf{flow convexity} to quantify asymmetric positioning risk and potential forced flows.}
\resumeItem{\textit{Keywords: COT Analysis, CTA Positioning, Time Series Momentum, Flow Convexity, Position Saturation.}}
\resumeItemListEnd

\resumeSubheading
{Funds Avenue}{Luxembourg}
{Risk Management Intern}{July 2024 - Dec 2024}

\resumeItemListStart
\resumeItem{Assessed portfolio risk using \textbf{stress tests} and \textbf{Value-at-Risk (VaR)} via Python/Excel models and presented risk reports to senior management.}
\resumeItem{Applied multi-factor risk frameworks aligned with \textbf{Axioma} and \textbf{Barra}-style models for factor exposure analysis and systematic variance decomposition.}
\resumeItem{\textit{Keywords: Risk Management, Value-at-Risk (VaR), Stress Testing, Portfolio Analysis, Python, Axioma, Barra.}}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXTRACURRICULAR PROJECTS----------
\section{Extracurricular Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{ENS / QRT Data Challenge - Asset Allocation Forecasting} $|$ \emph{Python, Machine Learning}}{Jun 2026}
\resumeProjectItemListStart
\resumeItem{Competing in an ENS-hosted data challenge set up by QRT to forecast portfolio movements from time-series and tabular data; achieved a \textbf{0.52 public test score} and currently rank in the \textbf{top 10\% on the private test leaderboard}.}
\resumeProjectItemListEnd

\resumeProjectHeading
{\textbf{Guéant-Lehalle-Fernandez-Tapia (GLFT) Market Making Model} $|$ \emph{Python, NumPy, Pandas, Polars, SciPy}}{Sep 2025}
\resumeProjectItemListStart
\resumeItem{Implemented the closed-form optimal quoting strategy under inventory constraints from the Guéant-Lehalle-Fernandez-Tapia market making framework, an extension of Avellaneda-Stoikov.}
\resumeItem{Built a realistic backtest including Poisson fills, inventory dynamics, maker fees, latency and stochastic slippage.}
\resumeProjectItemListEnd

\resumeProjectHeading
{\textbf{Portfolio Optimization Strategy} $|$ \emph{Python, NumPy, SciPy, Matplotlib}}{Jan 2024}
\resumeProjectItemListStart
\resumeItem{Constructed optimal portfolios using Mean-Variance Optimization via \texttt{scipy.optimize} to maximize the Sharpe Ratio.}
\resumeItem{Simulated thousands of portfolios (Monte Carlo) to visualize the Efficient Frontier and the Capital Market Line (CML).}
\resumeProjectItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION----------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{Neoma Business School}{Rouen, France}
{MSc Corporate Finance \& Investment Banking $|$ \textbf{GPA: 4.0/4.0}}{Oct 2023 - Dec 2024}
\resumeItemListStart
\resumeItem{Double degree with ESIGELEC.}
\resumeItem{Thesis: \textbf{Stochastic Models and Real Options in Corporate Valuation}.}
\resumeItem{\textbf{Key Modules:} Financial Engineering, Advanced Corporate Finance, Mergers \& Acquisitions, Corporate Strategies.}
\resumeItemListEnd

\resumeSubheading
{ESIGELEC Engineering School}{Rouen, France}
{Engineering Degree in Financial Engineering (after PTSI Preparatory Classes) $|$ \textbf{Top 10\% of Class}}{Sep 2018 - Dec 2024}
\resumeItemListStart
\resumeItem{\textbf{Key Modules:} Advanced Probability, Machine Learning, Monte Carlo Simulation, Applied Statistics for Finance.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------ADDITIONAL TRAINING----------
\section{Additional Training}
\resumeSubHeadingListStart

\resumeSubheading
{MIT - edX}{Online}
{Quantitative Finance \& Machine Learning Certifications}{}
\resumeItemListStart
\resumeItem{\textbf{Mathematical Methods for Quantitative Finance:} Probability, stochastic processes (discrete \& continuous), It\^o calculus, time series.}
\resumeItem{\textbf{Machine Learning with Python:} Linear models, clustering, recommender systems, CNN, generative models, reinforcement learning, NLP.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SKILLS----------
\section{Skills \& Interests}
\begin{itemize}[leftmargin=0.20in, label={}]
\small{\item{
\textbf{Languages}: French (native), English (C1) \\
\textbf{Programming}: Python (NumPy, pandas, scipy, scikit-learn, Polars), SQL \\
\textbf{IT}: Microsoft Office, \LaTeX \\
\textbf{Interests}: Fencing (Regional Level \& Referee), French History
}}
\end{itemize}

\end{document}
